---
title: "HAI-Net ICU Annual Report"
format:
  html:
    toc: true
    toc-depth: 3
  docx: default
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

if (requireNamespace("devtools", quietly = TRUE)) {
  devtools::load_all(quiet = TRUE)
}

report_data <- prepare_report_data()
report_tables <- hicu_prepare_report_tables(report_data)
report_summaries <- hicu_prepare_report_summaries(report_data)
```

## Participation Overview

In `r report_data$year`, `r report_summaries$participation$country_count` countries reported data from `r report_summaries$participation$hospital_count` hospitals and `r report_summaries$participation$icu_count` ICUs. ICU characteristics are shown in @tbl-icu-characteristics.

The median size of participating ICUs was `r report_summaries$participation$unit_size_median` beds, ranging from `r report_summaries$participation$unit_size_min` to `r report_summaries$participation$unit_size_max` beds.

Of `r report_summaries$participation$patient_count` patients staying in an ICU for more than two days, `r report_summaries$participation$patients_with_hai` patients (`r report_summaries$participation$patients_with_hai_percent`%) presented with at least one healthcare-associated infection.

## ICU Characteristics

```{r}
#| label: tbl-icu-characteristics
#| tbl-cap: "ICU characteristics by country/network"

knitr::kable(report_tables$icu_characteristics)
```

## Patient Demographics

```{r}
#| label: tbl-patient-demographics
#| tbl-cap: "Patient demographics by country/network"

knitr::kable(report_tables$patient_demographics)
```

## Infection Outcomes

```{r}
#| label: tbl-infection-outcomes
#| tbl-cap: "Infection outcomes by country/network"

knitr::kable(report_tables$infection_outcomes)
```

## ICU-Acquired Pneumonia

Of `r report_summaries$pneumonia$cases` pneumonia episodes reported, `r report_summaries$pneumonia$intubation_associated_percent`% were associated with intubation. Among patients staying in an ICU for more than two days, `r report_summaries$pneumonia$patient_percent`% were affected by at least one pneumonia episode.

The incidence of pneumonia was `r report_summaries$pneumonia$incidence` episodes per 1 000 patient-days. Country/network incidence is shown in @tbl-pn-incidence and intubation-associated pneumonia in @tbl-iap.

```{r}
#| label: tbl-pn-incidence
#| tbl-cap: "Pneumonia incidence by country/network"

knitr::kable(report_tables$pn_incidence)
```

```{r}
#| label: tbl-iap
#| tbl-cap: "Intubation-associated pneumonia by country/network"

knitr::kable(report_tables$iap)
```

The most frequently isolated microorganisms in ICU-acquired pneumonia episodes were `r report_summaries$pneumonia$top_isolates_text`. The full microorganism distribution is shown in @tbl-pn-microorganisms.

```{r}
#| label: tbl-pn-microorganisms
#| tbl-cap: "Most frequently isolated microorganisms in pneumonia episodes"

knitr::kable(report_tables$pn_microorganisms)
```

## ICU-Acquired Bloodstream Infections

A total of `r report_summaries$bloodstream$cases` ICU-acquired bloodstream infection episodes were reported. On average, bloodstream infections occurred in `r report_summaries$bloodstream$patient_percent`% of patients staying in an ICU for more than two days.

The mean incidence density per ICU was `r report_summaries$bloodstream$mean_icu_incidence` bloodstream infection episodes per 1 000 patient-days. Country/network incidence is shown in @tbl-bsi-incidence, with primary BSI, CRI3, and CVC-associated BSI details in @tbl-prbsi, @tbl-cri3, and @tbl-cvc-associated-bsi.

```{r}
#| label: tbl-bsi-incidence
#| tbl-cap: "Bloodstream infection incidence by country/network"

knitr::kable(report_tables$bsi_incidence)
```

```{r}
#| label: tbl-prbsi
#| tbl-cap: "Primary bloodstream infection incidence by country/network"

knitr::kable(report_tables$prbsi)
```

```{r}
#| label: tbl-cri3
#| tbl-cap: "CRI3 incidence by country/network"

knitr::kable(report_tables$cri3)
```

```{r}
#| label: tbl-cvc-associated-bsi
#| tbl-cap: "CVC-associated bloodstream infection by country/network"

knitr::kable(report_tables$cvc_associated_bsi)
```

Additional catheter-related and CVC-associated bloodstream infection summaries are shown in @tbl-catheter-related-bsi, @tbl-total-crbsi, @tbl-eu-cvc-associated-bsi, and @tbl-clabsi-by-country.

```{r}
#| label: tbl-catheter-related-bsi
#| tbl-cap: "Catheter-related bloodstream infection by country/network"

knitr::kable(report_tables$catheter_related_bsi)
```

```{r}
#| label: tbl-total-crbsi
#| tbl-cap: "Total catheter-related bloodstream infection by country/network"

knitr::kable(report_tables$total_crbsi)
```

```{r}
#| label: tbl-eu-cvc-associated-bsi
#| tbl-cap: "EU/EEA CVC-associated bloodstream infection summary"

knitr::kable(report_tables$eu_cvc_associated_bsi)
```

```{r}
#| label: tbl-clabsi-by-country
#| tbl-cap: "CLABSI incidence by country/network"

knitr::kable(report_tables$clabsi_by_country)
```

The most frequently isolated microorganisms in bloodstream infection episodes were `r report_summaries$bloodstream$top_isolates_text`. The full microorganism distribution is shown in @tbl-bsi-microorganisms.

```{r}
#| label: tbl-bsi-microorganisms
#| tbl-cap: "Most frequently isolated microorganisms in bloodstream infection episodes"

knitr::kable(report_tables$bsi_microorganisms)
```

## ICU-Acquired Urinary Tract Infections

A total of `r report_summaries$urinary_tract$cases` ICU-acquired urinary tract infection episodes were reported. On average, urinary tract infections occurred in `r report_summaries$urinary_tract$patient_percent`% of patients staying in an ICU for more than two days.

The mean incidence density per ICU was `r report_summaries$urinary_tract$mean_icu_incidence` urinary tract infection episodes per 1 000 patient-days. Country/network incidence is shown in @tbl-uti-incidence.

```{r}
#| label: tbl-uti-incidence
#| tbl-cap: "Urinary tract infection incidence by country/network"

knitr::kable(report_tables$uti_incidence)
```

The most frequently isolated microorganisms in urinary tract infection episodes were `r report_summaries$urinary_tract$top_isolates_text`. The full microorganism distribution is shown in @tbl-uti-microorganisms.

```{r}
#| label: tbl-uti-microorganisms
#| tbl-cap: "Most frequently isolated microorganisms in urinary tract infection episodes"

knitr::kable(report_tables$uti_microorganisms)
```

## Antimicrobial Resistance

Reported percentages of resistant isolates in selected bacteria associated with ICU-acquired infections cover `r report_summaries$antimicrobial_resistance$indicator_count` indicators, including `r report_summaries$antimicrobial_resistance$indicator_text`. Country/network results are shown in @tbl-antimicrobial-resistance.

```{r}
#| label: tbl-antimicrobial-resistance
#| tbl-cap: "Antimicrobial resistance indicators by country/network"

knitr::kable(report_tables$antimicrobial_resistance)
```

## Antimicrobial Use

Antimicrobial use summaries by selected antimicrobial group and indication are shown in @tbl-antimicrobial-groups and @tbl-antimicrobial-indications.

```{r}
#| label: tbl-antimicrobial-groups
#| tbl-cap: "Antimicrobial use by selected antimicrobial group and country/network"

knitr::kable(report_tables$antimicrobial_groups)
```

```{r}
#| label: tbl-antimicrobial-indications
#| tbl-cap: "Antimicrobial use indication by country/network"

knitr::kable(report_tables$antimicrobial_indications)
```

## Structure And Process Indicators

Structure and process indicators for infection prevention and control in intensive care units are shown in @tbl-structure-indicators and @tbl-process-indicators.

```{r}
#| label: tbl-structure-indicators
#| tbl-cap: "Structure and process indicators for infection prevention and control in intensive care units"

knitr::kable(report_tables$structure_indicators)
```

```{r}
#| label: tbl-process-indicators
#| tbl-cap: "Process indicators assessed through chart review"

knitr::kable(report_tables$process_indicators)
```
