---
title: "HAIICU2023"
author: "DP"
date: "8 June 2025"
output:
  word_document: default
---

**HAIICU 2023 Report**

```{r, echo=FALSE, warning=FALSE, message=FALSE}

library(dplyr)
library(knitr)
library(here)
library(flextable)

make_report_table <- function(x, caption = NULL, font_size = 8, width = 0.9) {
  x <- as.data.frame(x)

  if (knitr::is_html_output()) {
    return(knitr::kable(x, caption = caption, format = "html"))
  }

  width <- min(max(width, 0.1), 1.0)

  ft <- flextable::flextable(x)
  ft <- flextable::theme_vanilla(ft)
  ft <- flextable::set_table_properties(ft, width = width, layout = "autofit")
  ft <- flextable::autofit(ft)
  ft <- flextable::fontsize(ft, size = font_size, part = "all")
  ft <- flextable::align(ft, align = "left", part = "all")
  if (!is.null(caption)) {
    ft <- flextable::set_caption(ft, caption = caption)
  }
  ft
}

source(here("R", "haiicu_functions.r")) 
year <- Sys.getenv("HAINET_YEAR", unset = "2023")
DATA_DIR <- here("data", "raw", year)
OUTPUT_DIR <- here("outputs", year)

haiicu_intub<-read_output_rds("haiicu_percintub.Rda")
haiicudenscountr<-read_output_rds("haiicuiapdens.Rda")
haiicu_level1_all<-load_output_rds("haiicu_level1_all.Rda")
haiicu_pt<-read_output_rds("haiicu_pt_unit.Rda")
haiicu_pt_inf_all<-read_output_rds("haiicu_pt_inf_all.Rda")
haiicuall2<-read_output_rds("haiicuall2.Rda")
IAPtable<-read_output_rds("IAPtable.Rda")
unit_clabsi<-read_output_rds("unit_clabsi.Rda")
haiicu_unitall_bsi<-read_output_rds("haiicu_unitall_bsi.Rda")
PNinc_country<-read_output_rds("PNinc_country.Rda")
BSIinc_country<-read_output_rds("BSIinc_country.Rda")
UTIinc_country<-read_output_rds("UTIinc_country.Rda")
PNinc_EU<-read_output_rds("PNinc_EU.Rda")
BSIinc_EU<-read_output_rds("BSIinc_EU.Rda")
UTIinc_EU<-read_output_rds("UTIinc_EU.Rda")
#haiicu_unitall_bsi<-filter(haiicu_unitall_bsi,InfectionSite=="CRI1"|InfectionSite=="CRI2")
haiicu_unit_expcvc<-read_output_rds("haiicu_unit_expcvc.Rda")
haiicu_country_expcvc<-read_output_rds("haiicu_country_expcvc.Rda")
haiicu_unit_bsidevadj<-read_output_rds("haiicu_unit_bsidevadj.Rda")
bsidevadj_bycountry<-read_output_rds("bsidevadj_bycountry.Rda")
CRBSItable<-read_output_rds("CRBSItable.Rda")
totcrbsitable<-read_output_rds("totcrbsitable.Rda")
haiicu_unit_bsidevadj_totcritable<-read_output_rds("unit_crbsi_table.Rda")
bsidevadj_totcritable_bycountry<-read_output_rds("totcrbsitable.Rda")
BSItable_group_top10_pc<-read_output_rds("BSItable_group_top10_pc.Rda")
haiicu_unitall_uti<-read_output_rds("haiicu_unitall_uti.Rda")
haiicu_unit_expuc<-read_output_rds("haiicu_unit_expuc.Rda")
haiicu_country_expuc<-read_output_rds("haiicu_country_expuc.Rda")
UTItable_group_top10_pc<-read_output_rds("UTItable_group_top10_pc.Rda")
haiicu_pt_uti<-read_output_rds("haiicu_pt_uti.Rda")
haiicu_aggr_uti<-read_output_rds("haiicu_aggr_uti.Rda")
PNtable_group_top10_pc<-read_output_rds("PNtable_group_top10_pc.Rda")
haiicu_aggr<-read_output_rds("haiicu_aggr.Rda")
resist<-read_output_rds("resist.Rda")
country_demogr<-read_output_rds("country_demogr.Rda")
country_unit_table<-read_output_rds("country_unit_table.Rda")
cri3table<-read_output_rds("cri3table.Rda")
cvcasbsitable<-read_output_rds("cvcasbsitable.Rda")
prbsi_table<-read_output_rds("prbsi_table.Rda")
clabsi_bycountry<-read_output_rds("clabsi_bycountry.Rda")
haiicu_unit_bsidevadj_cvcasbsi<-read_output_rds("haiicu_unit_bsidevadj_cvcasbsitable.Rda")
country_ab_table<-read_output_rds("country_ab_table.Rda")
country_ab_ind<-read_output_rds("country_ab_ind.Rda")
country_deno_7d<-read_output_rds("country_deno_7d.Rda")
country_ind<-read_output_rds("country_ind.Rda")
InfOutc<-read_output_rds("InfOutc.Rda")

```

<!--Participating units-->
<!--Participating units-->
In `r year` , `r nlevels(as.factor(haiicu_level1_all$ReportingCountry))` countries reported data from `r nlevels(as.factor(haiicu_level1_all$HospitalIdGlobal))` hospitals and `r nlevels(as.factor(haiicu_level1_all$UnitIdGlobal))` ICUs:
```{r, echo=FALSE, comment=""}
Total=sum
ReportingCountries<-addmargins(table(haiicu_level1_all$Subject, haiicu_level1_all$ReportingCountry), 2, FUN=Total)
ReportingCountries
```
The speciality of the participating ICUs were:
```{r, echo=FALSE, comment=""}
table(haiicu_level1_all$Subject, haiicu_level1_all$UnitSpecialty)
```
The median size of the participating ICUs was `r median(as.numeric(haiicu_level1_all$UnitSize),na.rm=TRUE)` beds ranging from  `r min(as.numeric(haiicu_level1_all$UnitSize),na.rm=TRUE)` to `r max(as.numeric(haiicu_level1_all$UnitSize),na.rm=TRUE)`.

Of `r nrow(haiicu_pt)` patients staying in an ICU for more than two days (patient-based data), `r haiicu_pt_inf_all%>%filter(hasHai==TRUE)%>%distinct(Id,.keep_all=TRUE)%>%nrow()` patients (`r round((haiicu_pt_inf_all%>%filter(hasHai==TRUE)%>%distinct(Id,.keep_all=TRUE)%>%nrow())/nrow(haiicu_pt), digits=3) * 100`%) presented with at least one HAI.

## ICU-acquired pneumonia
Of `r sum(grepl("PN",haiicu_pt_inf_all$InfectionSite))` cases of pneumonia reported, `r round(sum(haiicu_pt_inf_all$Intubation=="Y" & grepl("PN",haiicu_pt_inf_all$InfectionSite))/sum(grepl("PN",haiicu_pt_inf_all$InfectionSite)),digits=3)*100`% were associated with intubation. Among patients staying in an ICU for more than two days, `r round(sum(grepl("PN",haiicu_pt_inf_all$InfectionSite))/sum(!haiicu_pt_inf_all$dupl_pat)*100,digits=2)`% were affected by at least one episode pneumonia. 

```{r, echo=FALSE, results='hide'}
patient_days<-sum(as.numeric(haiicu_pt_inf_all$lengthofstay[! haiicu_pt_inf_all$dupl_pat]),na.rm=TRUE)
pn<-haiicu_intub$PN
pn_cases<-sum(pn,na.rm=TRUE)
patient_days_all<-sum(as.numeric(haiicu_intub$NumPatDaysUnit2d),na.rm=TRUE)
per_intubgroup<-group_by(haiicu_intub,intubgroup)
PNinc_byintubgroup<-summarise(per_intubgroup,meanPNinc=round(mean(incdens[incdens!=Inf],na.rm=TRUE),digits=2))


```

The incidence of pneumonia was `r round(sum(grepl("PN", haiicu_pt_inf_all$InfectionSite),na.rm=TRUE)/(patient_days)*1000, digits=2)` episodes per 1000 patient days (Table 1).

The mean incidence density per ICU was `r round(mean(haiicu_intub$incdens[haiicu_intub$incdens!=Inf],na.rm=TRUE), digits=2)` pneumonia episodes per 1 000 patient-days (ICU IQR:`r quantile(haiicu_intub$incdens,c(.25),na.rm=TRUE)`-`r round(quantile(haiicu_intub$incdens,c(.75),na.rm=TRUE),digits=2)` ), varying from `r PNinc_byintubgroup[1,"meanPNinc"]` in ICUs with less than 30% intubated patients to `r PNinc_byintubgroup[2,"meanPNinc"]` in ICUs with 30-59% intubated patients, and `r PNinc_byintubgroup[3,"meanPNinc"]` in ICUs with more than 60% intubated patients.

```{r, echo=FALSE, results='asis'}
make_report_table(PNinc_country, caption = "Pneumonia incidence by country")
make_report_table(PNinc_EU, caption = "Pneumonia incidence in the EU")
```

In patient-based surveillance, the mean device-adjusted rate was `r round(mean(round(haiicudenscountr$iapincintubdays,digits=2)),digits=2)` intubation-associated pneumonia episodes
per 1 000 intubation-days and varied between `r min(IAPtable$avgiaprate)` (`r IAPtable$ReportingCountry[IAPtable$avgiaprate==min(IAPtable$avgiaprate)]`), and `r max(IAPtable$avgiaprate)` per 1 000 intubation-days
(`r IAPtable$ReportingCountry[IAPtable$avgiaprate==max(IAPtable$avgiaprate)]`) (Table 2).

```{r, echo=FALSE, results='asis'}
make_report_table(IAPtable, caption = "Intubation-associated pneumonia table")
```
 
 
The most frequently isolated microorganisms in ICU-acquired pneumonia episodes were  *`r PNtable_group_top10_pc$Isolate[PNtable_group_top10_pc$totalpc==max(PNtable_group_top10_pc$totalpc)]`*   followed by *`r PNtable_group_top10_pc$Isolate[2]`*, *`r PNtable_group_top10_pc$Isolate[3]`* and *`r PNtable_group_top10_pc$Isolate[4]`* (Table 3).


`r make_report_table(PNtable_group_top10_pc, caption = 'Top microorganisms in pneumonia episodes')` 


## ICU-acquired blood stream infections
A total of `r sum(grepl("BSI|CRI3",haiicu_pt_inf_all$InfectionSite))` cases of ICU-acquired bloodstream infection were reported. On average, ICU-acquired blood stream infections occurred in `r round(sum(grepl("BSI|CRI3",haiicu_pt_inf_all$InfectionSite))/sum(!haiicu_pt_inf_all$dupl_pat)*100,digits=2)`% of patients staying in an ICU for more than two days. The mean incidence density per ICU was `r round((mean(haiicuall2$BSI_incdens,na.rm=TRUE)),digits=2)` bloodstream infection episodes per 1 000 patient-days (ICU IQR: `r round(quantile(haiicuall2$BSI_incdens,c(.25),na.rm=TRUE),digits=2)`-`r round(quantile(haiicuall2$BSI_incdens,c(.75),na.rm=TRUE),digits=2)`)(Table 4).The mean incidence density per ICU was `r round(sum(haiicu_aggr$PRBSI,na.rm=TRUE)/(sum(as.numeric(haiicu_aggr$NumPatDaysUnit2d),na.rm=TRUE))*1000,digits=2)` primary bloodstream infection episodes per 1 000 patient-days (ICU IQR: `r quantile(haiicu_aggr$prbsi_incdens,c(.25),na.rm=TRUE)`-`r round(quantile(haiicu_aggr$prbsi_incdens,c(.75),na.rm=TRUE),digits=2)`). Bloodstream infections were catheter-related in `r round((sum(grepl("^C",haiicu_unitall_bsi$BSIOrigin))+sum(haiicu_unitall_bsi$InfectionSite=="CRI3"))/summarise(haiicu_unitall_bsi,n=n())*100,digits=2)`% of cases, secondary to another infection in `r round(sum(grepl("^S",haiicu_unitall_bsi$BSIOrigin))/summarise(haiicu_unitall_bsi,n=n())*100,digits=2)`% of cases, and of unknown origin in `r round(sum(grepl("^$|UO|UNK",haiicu_unitall_bsi$BSIOrigin))/summarise(haiicu_unitall_bsi,n=n())*100,digits=2)`% of cases. When the bloodstream infection was secondary to another infection, the primary infection site was pulmonary in `r round(sum(grepl("S-PUL",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%, gastrointestinal (`r round(sum(grepl("S-DIG",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), the urinary tract (`r round(sum(grepl("S-UTI",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), a surgical site (`r round(sum(grepl("S-SSI",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), skin and soft tissues (`r round(sum(grepl("S-SST",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), and other in the remaining `r round(sum(grepl("S-OTH",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%. 

```{r, echo=FALSE, results='asis'}
make_report_table(BSIinc_country, caption = "BSI incidence by country")
make_report_table(BSIinc_EU, caption = "BSI incidence in the EU")
```


In patient-based surveillance, the central vascular catheter (CVC) utilisation rate was on average `r round(mean(haiicu_unit_bsidevadj_totcritable$unitexpdays,na.rm=TRUE)/mean(as.numeric(haiicu_unit_bsidevadj_totcritable$NumPatDaysUnit2d[haiicu_unit_bsidevadj_totcritable$ReportingCountry!="LU"]),na.rm=TRUE)*1000,digits=0)` CVC-days per 1 000 patientdays.It was the lowest (`r min(haiicu_country_expcvc$utilrate)*1000`) in `r haiicu_country_expcvc$ReportingCountry[haiicu_country_expcvc$utilrate==min(haiicu_country_expcvc$utilrate)]` and the highest (`r max(haiicu_country_expcvc$utilrate[haiicu_country_expcvc$ReportingCountry!="LU"])*1000`) in `r haiicu_country_expcvc$ReportingCountry[haiicu_country_expcvc$utilrate==max(haiicu_country_expcvc$utilrate[haiicu_country_expcvc$ReportingCountry!="LU"])]`. The mean device-adjusted rate in patients staying in an ICU for more than two days was `r round(mean(unit_clabsi$clabsiinc, na.rm=TRUE),digits=2)` CVC-associated bloodstream infection episodes per 1 000 CVC-days (ICU IQR: `r quantile(unit_clabsi$clabsiinc,c(.25),na.rm=TRUE)`-`r quantile(unit_clabsi$clabsiinc,c(.75), na.rm=TRUE)`), varying from `r min(clabsi_bycountry$countrclabsiinc)` in `r clabsi_bycountry$ReportingCountry[clabsi_bycountry$countrclabsiinc==min(clabsi_bycountry$countrclabsiinc)]` to `r max(clabsi_bycountry$countrclabsiinc)` in `r clabsi_bycountry$ReportingCountry[clabsi_bycountry$countrclabsiinc==max(clabsi_bycountry$countrclabsiinc)]` (Table 5). 

```{r, echo=FALSE, results='asis'}
make_report_table(cvcasbsitable, caption = "CVC-associated BSI table")
```

The most frequently isolated microorganisms in bloodstream infection episodes were  `r BSItable_group_top10_pc$Isolate[1]`   followed by `r BSItable_group_top10_pc$Isolate[2]`, `r BSItable_group_top10_pc$Isolate[3]` and `r BSItable_group_top10_pc$Isolate[4]` (Table 6).


`r make_report_table(BSItable_group_top10_pc, caption = 'Top microorganisms in bloodstream infection episodes')`

```{r, echo=FALSE, results='hide'}
haiicuall2<-haiicuall2%>%filter(!ReportingCountry%in%c("DE","FR"))
```

## ICU-acquired urinary tract infections
A total of `r sum(grepl("UTI",haiicu_pt_inf_all$InfectionSite))` cases of ICU-acquired urinary infection were reported. On average, ICU-acquired urinary infections occurred in `r round(sum(grepl("UTI",haiicu_pt_uti$InfectionSite))/sum(!haiicu_pt_uti$dupl_pat)*100,digits=2)`% of patients staying in an ICU for more than two days,  with `r round(sum(haiicu_pt_uti$InvasiveDevice=="Y" & grepl("^UTI",haiicu_pt_uti$InfectionSite))/sum(grepl("^UTI",haiicu_pt_uti$InfectionSite) & haiicu_pt_uti$UrinaryCatheter!="Unk"),digits=3)*100`% of UTI episodes being associated with the use of a urinary catheter. The mean incidence density per ICU was `r round((mean(haiicuall2$UTI_incdens,na.rm=TRUE)),digits=2)` urinary tract infection episodes per 1 000 patient-days (ICU IQR: `r quantile(haiicuall2$UTI_incdens,c(.25),na.rm=TRUE)`-`r round(quantile(haiicuall2$UTI_incdens,c(.75),na.rm=TRUE),digits=2)`)(Table 7). On average, urinary catheters were used in `r round(mean(haiicu_unit_expuc$unitexpdays,na.rm=TRUE)/mean(as.numeric(haiicu_unit_expuc$NumPatDaysUnit2d),na.rm=TRUE)*100,digits=0)`% of the patient-days. The mean device-adjusted rate in patients staying in an ICU for more than two days was `r round(mean(haiicu_unit_expuc$utidevadj,na.rm=TRUE),digits=2)` catheter-associated urinary tract infection episodes per 1 000 catheter-days (ICU IQR: `r quantile(haiicu_unit_expuc$utidevadj,c(.25),na.rm=TRUE)`-`r quantile(haiicu_unit_expuc$utidevadj,c(.75),na.rm=TRUE)`)

```{r, echo=FALSE, results='asis'}
make_report_table(UTIinc_country, caption = "UTI incidence by country")
make_report_table(UTIinc_EU, caption = "UTI incidence in the EU")
```

The most frequently isolated microorganisms in urinary tract infection episodes were  `r UTItable_group_top10_pc$Isolate[1]`   followed by `r UTItable_group_top10_pc$Isolate[2]`, `r UTItable_group_top10_pc$Isolate[3]` and `r UTItable_group_top10_pc$Isolate[4]` (Table 8).

`r make_report_table(UTItable_group_top10_pc, caption = 'Top microorganisms in urinary tract infection episodes')`


## Antimicrobial resistance
<!-- exclude data from Germany r resist<-filter(resist,!RecordId %in% c(23007784:23033121))--> The reported percentages of resistant isolates in selected bacteria associated with ICU-acquired infections were: oxacillin resistance (MRSA) in  `r round(100*sum(resist$ResultIsolate=="STAAUR" & resist$SIR %in% c("R","IR") & resist$Antibiotic=="OXA",na.rm=TRUE)/sum(resist$ResultIsolate=="STAAUR" & resist$Antibiotic %in% c("OXA"),na.rm=TRUE),digits=1)`% of *S. aureus* isolates (n=`r sum(resist$ResultIsolate=="STAAUR" & resist$Antibiotic %in% c("OXA"))`); vancomycin resistance in  `r round(100*sum(resist$Isolate=="Enterococcus" & resist$SIR=="R" & resist$Antibiotic %in% c("GLY"),na.rm=TRUE)/sum(resist$Isolate=="Enterococcus" & resist$Antibiotic%in% c("GLY"),na.rm=TRUE),digits=1)`% of *Enterococcus* spp. isolates (n=`r  sum(resist$Isolate=="Enterococcus" & resist$Antibiotic%in% c("GLY"),na.rm=TRUE)`);ceftazidime resistance in   `r round(100*sum(resist$ResultIsolate=="PSEAER" & resist$SIR=="R" & resist$Antibiotic=="C3G",na.rm=TRUE)/sum(resist$ResultIsolate=="PSEAER" & resist$Antibiotic %in% c("C3G"),na.rm=TRUE),digits=1)`% of *P. aeruginosa* isolates (n=`r sum(resist$ResultIsolate=="PSEAER" & resist$Antibiotic%in% c("C3G"))`);and resistance to third-generation cephalosporins in  `r round(100*sum(resist$ResultIsolate=="ESCCOL" & resist$SIR=="R" & resist$Antibiotic=="C3G",na.rm=TRUE)/sum(resist$ResultIsolate=="ESCCOL" & resist$Antibiotic%in% c("C3G"),na.rm=TRUE),digits=1)`% of *E. coli* isolates(n=`r sum(resist$ResultIsolate=="ESCCOL" & resist$Antibiotic%in% c("C3G"))`),  `r round(100*sum(resist$Isolate=="Klebsiellas" & resist$SIR=="R" & resist$Antibiotic=="C3G",na.rm=TRUE)/sum(resist$Isolate=="Klebsiellas" & resist$Antibiotic%in% c("C3G"),na.rm=TRUE),digits=1)`%of *Klebsiella* spp. isolates (n=`r  sum(resist$Isolate=="Klebsiellas" & resist$Antibiotic%in% c("C3G"),na.rm=TRUE)`) and  `r round(100*sum(resist$Isolate=="Enterobacter" & resist$SIR=="R" & resist$Antibiotic=="C3G",na.rm=TRUE)/sum(resist$Isolate=="Enterobacter" & resist$Antibiotic%in% c("C3G"),na.rm=TRUE),digits=1)`% of *Enterobacter* spp. isolates (n=`r  sum(resist$Isolate=="Enterobacter" & resist$Antibiotic%in% c("C3G"),na.rm=TRUE)`). Carbapenem resistance was reported in  `r round(100*sum(resist$Isolate=="Klebsiellas" & resist$SIR=="R" & resist$Antibiotic=="CAR",na.rm=TRUE)/sum(resist$Isolate=="Klebsiellas" & resist$Antibiotic %in% c("CAR"),na.rm=TRUE),digits=1)`% of *Klebsiella* spp. isolates (n=`r  sum(resist$Isolate=="Klebsiellas" & resist$Antibiotic%in% c("CAR"),na.rm=TRUE)`),  `r round(100*sum(resist$ResultIsolate=="ESCCOL" & resist$SIR=="R" & resist$Antibiotic=="CAR",na.rm=TRUE)/sum(resist$ResultIsolate=="ESCCOL" & resist$Antibiotic%in% c("CAR"),na.rm=TRUE),digits=1)`% of *E. coli* isolates (n=`r sum(resist$ResultIsolate=="ESCCOL" & resist$Antibiotic%in% c("CAR"))`),  `r round(100*sum(resist$Isolate=="Enterobacter" & resist$SIR=="R" & resist$Antibiotic=="CAR",na.rm=TRUE)/sum(resist$Isolate=="Enterobacter" & resist$Antibiotic%in% c("CAR"),na.rm=TRUE),digits=1)`% of *Enterobacter* spp. isolates (n=`r  sum(resist$Isolate=="Enterobacter" & resist$Antibiotic%in% c("CAR"),na.rm=TRUE)`),  `r round(100*sum(resist$ResultIsolate=="PSEAER" & resist$SIR=="R" & resist$Antibiotic=="CAR",na.rm=TRUE)/sum(resist$ResultIsolate=="PSEAER" & resist$Antibiotic%in% c("CAR"),na.rm=TRUE),digits=1)`% of *P. aeruginosa* isolates (n=`r sum(resist$ResultIsolate=="PSEAER" & resist$Antibiotic%in% c("CAR"))`) and  `r round(100*sum(resist$ResultIsolate=="ACIBAU" & resist$SIR=="R" & resist$Antibiotic=="CAR")/sum(resist$ResultIsolate=="ACIBAU" & resist$Antibiotic%in% c("CAR")),digits=1)`% of *Acinetobacter baumanii* (n=`r sum(resist$ResultIsolate=="ACIBAU" & resist$Antibiotic%in% c("CAR"))`) isolates.


##Annex 2

## Table A2. ICU characteristics 
`r make_report_table(country_unit_table, caption = 'Table A2. ICU characteristics')`

## Table A3. Patient demographics
`r make_report_table(country_demogr, caption = 'Table A3. Patient demographics')`

## Table A4. Primary BSI by country
`r make_report_table(prbsi_table, caption = 'Table A4. Primary BSI by country')`

## Table A5. CRBSI by country
`r make_report_table(cri3table, caption = 'Table A5. CRBSI by country')`

## Table A6. CVC-associated BSI by country
`r make_report_table(bsidevadj_totcritable_bycountry, caption = 'Table A6. CVC-associated BSI by country')`

## Table 9. Antimicrobial use selected antimicrobial groups, by country
`r make_report_table(country_ab_table, caption = 'Table 9. Antimicrobial use selected antimicrobial groups, by country')`

## Table 9. Antimicrobial use indication, by country
`r make_report_table(country_ab_ind, caption = 'Table 9. Antimicrobial use indication, by country')`

## Table 10. Healthcare-associated infection outcome by country
`r make_report_table(InfOutc, caption = 'Table 10. Healthcare-associated infection outcome by country')`

## Table 11. Structure and process indicators for infection prevention and control in intensive care units 
`r make_report_table(country_deno_7d, caption = 'Table 11. Structure and process indicators for infection prevention and control in intensive care units')`

## Table 12. Process indicators assessed through chart review
`r make_report_table(country_ind, caption = 'Table 12. Process indicators assessed through chart review')`
