---
title: "ICU-acquired bloodstream infections in HAIICU 2023 "
format: html
---

```{r}
#| label: setup
#| include: false
#| cache: false

library(dplyr)
library(knitr)

source("../../R/_report_setup.r")
source("../../R/_lookups.r")

n_bsi <- nrow(haiicu_unitall_bsi)


```

## ICU-acquired blood stream infections
A total of `r sum(grepl("BSI|CRI3",haiicu_pt_inf_all$InfectionSite))` cases of ICU-acquired bloodstream infection were reported. On average, ICU-acquired blood stream infections occurred in `r round(sum(grepl("BSI|CRI3",haiicu_pt_inf_all$InfectionSite))/sum(!haiicu_pt_inf_all$dupl_pat)*100,digits=2)`% of patients staying in an ICU for more than two days. The mean incidence density per ICU was `r round((mean(haiicuall2$BSI_incdens,na.rm=TRUE)),digits=2)` bloodstream infection episodes per 1 000 patient-days (ICU IQR: `r round(quantile(haiicuall2$BSI_incdens,c(.25),na.rm=TRUE),digits=2)`-`r round(quantile(haiicuall2$BSI_incdens,c(.75),na.rm=TRUE),digits=2)`)(Table 4).The mean incidence density per ICU was `r round(sum(haiicu_aggr$PRBSI,na.rm=TRUE)/(sum(as.numeric(haiicu_aggr$NumPatDaysUnit2d),na.rm=TRUE))*1000,digits=2)` primary bloodstream infection episodes per 1 000 patient-days (ICU IQR: `r quantile(haiicu_aggr$prbsi_incdens,c(.25),na.rm=TRUE)`-`r round(quantile(haiicu_aggr$prbsi_incdens,c(.75),na.rm=TRUE),digits=2)`). Bloodstream infections were catheter-related in `r round((sum(grepl("^C",haiicu_unitall_bsi$BSIOrigin))+sum(haiicu_unitall_bsi$InfectionSite=="CRI3"))/n_bsi * 100,digits=2)`% of cases, secondary to another infection in `r round(sum(grepl("^S",haiicu_unitall_bsi$BSIOrigin))/n_bsi * 100,digits=2)`% of cases, and of unknown origin in `r round(sum(grepl("^$|UO|UNK",haiicu_unitall_bsi$BSIOrigin))/n_bsi * 100,digits=2)`% of cases. When the bloodstream infection was secondary to another infection, the primary infection site was pulmonary in `r round(sum(grepl("S-PUL",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%, gastrointestinal (`r round(sum(grepl("S-DIG",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), the urinary tract (`r round(sum(grepl("S-UTI",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), a surgical site (`r round(sum(grepl("S-SSI",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), skin and soft tissues (`r round(sum(grepl("S-SST",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%), and other in the remaining `r round(sum(grepl("S-OTH",haiicu_unitall_bsi$BSIOrigin))/sum(grepl("S",haiicu_unitall_bsi$BSIOrigin))*100,digits=2)`%. 

## Country incidence

::: {.panel-tabset}
### Plot
```{r}
library(dplyr)
library(ggplot2)
library(scales)

bsi_plot_df <- BSIinc_country %>%
  transmute(
    country = ReportingCountry,
    rate = as.numeric(BSIinc)
  ) %>%
  filter(!is.na(country), !is.na(rate)) %>%
  arrange(rate) %>%
  mutate(country = factor(country, levels = country))

ggplot(bsi_plot_df, aes(x = country, y = rate)) +
  geom_segment(aes(xend = country, y = 0, yend = rate), linewidth = 0.7, color = "#9aa5b1") +
  geom_point(size = 2.8, color = "#0b6e4f") +
  coord_flip() +
  scale_y_continuous(labels = label_number(accuracy = 0.01)) +
  labs(
    x = NULL,
    y = "BSI incidence per 1,000 patient-days",
    title = "ICU-acquired BSI incidence by country"
  ) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank())


gt_tbl <- BSIinc_country_tbl |>
  gt::gt() |>
  apply_gt_labels(BSIinc_country_tbl) |>
  add_incidence_spanner(
    data = BSIinc_country_tbl,
    cols = inc_cols_bsi,
    title = "BSI incidence density",
    unit = "(episodes per 1 000 patient-days)"
  )|>
  style_gt_common(data = CLABSI_tbl)
gt_tbl

```

In patient-based surveillance, the central vascular catheter (CVC) utilisation rate was on average `r round(mean(haiicu_unit_bsidevadj_totcritable$unitexpdays,na.rm=TRUE)/mean(as.numeric(haiicu_unit_bsidevadj_totcritable$NumPatDaysUnit2d[haiicu_unit_bsidevadj_totcritable$ReportingCountry!="LU"]),na.rm=TRUE)*1000,digits=0)` CVC-days per 1 000 patientdays.It was the lowest (`r min(haiicu_country_expcvc$utilrate)*1000`) in `r haiicu_country_expcvc$ReportingCountry[haiicu_country_expcvc$utilrate==min(haiicu_country_expcvc$utilrate)]` and the highest (`r max(haiicu_country_expcvc$utilrate[haiicu_country_expcvc$ReportingCountry!="LU"])*1000`) in `r haiicu_country_expcvc$ReportingCountry[haiicu_country_expcvc$utilrate==max(haiicu_country_expcvc$utilrate[haiicu_country_expcvc$ReportingCountry!="LU"])]`. The mean device-adjusted rate in patients staying in an ICU for more than two days was `r round(mean(unit_clabsi$clabsiinc, na.rm=TRUE),digits=2)` CVC-associated bloodstream infection episodes per 1 000 CVC-days (ICU IQR: `r quantile(unit_clabsi$clabsiinc,c(.25),na.rm=TRUE)`-`r quantile(unit_clabsi$clabsiinc,c(.75), na.rm=TRUE)`), varying from `r min(clabsi_bycountry$countrclabsiinc)` in `r clabsi_bycountry$ReportingCountry[clabsi_bycountry$countrclabsiinc==min(clabsi_bycountry$countrclabsiinc)]` to `r max(clabsi_bycountry$countrclabsiinc)` in `r clabsi_bycountry$ReportingCountry[clabsi_bycountry$countrclabsiinc==max(clabsi_bycountry$countrclabsiinc)]` (Table 5). 

```{r, echo=FALSE}
gt_tbl <- CLABSI_tbl |>
  gt::gt() |>
  apply_gt_labels(CLABSI_tbl) |>
  add_incidence_spanner(
    data = CLABSI_tbl,
    cols = inc_cols_clabsi,
    title = "CLABSI incidence density",
    unit = "(episodes per 1 000 CVC-days)"
  )  |>
  style_gt_common(data = CLABSI_tbl)
gt_tbl
```

The most frequently isolated microorganisms in bloodstream infection episodes were  `r BSItable_group_top10_pc$Isolate[1]`   followed by `r BSItable_group_top10_pc$Isolate[2]`, `r BSItable_group_top10_pc$Isolate[3]` and `r BSItable_group_top10_pc$Isolate[4]` (Table 6).


```{r} 
BSItable_group_top10_pc %>%
  label_country_columns() %>%
  gt::gt()
```

```{r, echo=FALSE, results='hide'}
haiicuall2<-haiicuall2%>%filter(!ReportingCountry%in%c("DE","FR"))
```