---
title: "Participation in HAIICU 2023"
format: html
---

```{r}
#| label: setup
#| include: false
#| cache: false

library(dplyr)
library(knitr)

source("../../R/_report_setup.r")
source("../../R/_lookups.r")


```

<!--Participating units-->

## Participating countries
In `r REPORT_YEAR` , `r nlevels(allunits$ReportingCountry)` countries reported data from `r nlevels(allunits$HospitalIdGlobal)` hospitals and `r nlevels(allunits$UnitIdGlobal)` ICUs (@fig-participation-map). 



```{r}
library(dplyr)
library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(tibble)

to_iso2 <- function(x) ifelse(grepl("^IT", x), "IT", x)

standard_iso2 <- unique(to_iso2(as.character(haiicu_pt_inf_all$ReportingCountry)))
all_iso2 <- unique(to_iso2(as.character(allunits$ReportingCountry)))

protocol_df <- tibble(iso2 = all_iso2) %>%
  mutate(
    protocol = if_else(
      iso2 %in% standard_iso2,
      "Patient-based data ('standard protocol')",
      "Unit-based data ('light protocol')"
    )
  )

eu_eea_iso2 <- c(
  "AT","BE","BG","HR","CY","CZ","DK","EE","FI","FR","DE","GR","HU","IS","IE",
  "IT","LV","LI","LT","LU","MT","NL","NO","PL","PT","RO","SK","SI","ES","SE"
)

context_iso2 <- c(
  "GB","CH",          # UK, Switzerland
  "AL","BA","ME","MK","RS","XK"  # Western Balkans
)

world <- rnaturalearth::ne_countries(scale = 50, returnclass = "sf")

# Europe + nearby
map_df <- world %>%
  filter(continent == "Europe" | name %in% c("Turkey", "Cyprus")) %>%
  mutate(iso2 = iso_a2_eh) %>%   # IMPORTANT: better than iso_a2
  left_join(protocol_df, by = "iso2") %>%
  mutate(
    map_class = case_when(
      !is.na(protocol) ~ protocol,
      iso2 %in% context_iso2 ~ "Neighbouring countries",
      iso2 %in% eu_eea_iso2 ~ "EU/EEA non-participating",
      TRUE ~ "Other"
    )
  )
```
```{r}
#| label: fig-participation-map
#| fig-cap: "Participation in surveillance of healthcare-associated infections in intensive care units, EU/EEA, 2023"

ggplot(map_df) +
  geom_sf(aes(fill = map_class), color = "#A8A8A8", linewidth = 0.2) +
  scale_fill_manual(
    name = "Participating countries",
    values = c(
      "Patient-based data ('standard protocol')" = "#1F8A3B",
      "Unit-based data ('light protocol')" = "#9ACD5A",
      "Neighbouring countries" = "#E6E6E6",
      "EU/EEA non-participating" = "#CFCFCF",
      "Other" = "#D9D9D9"
    ),
    breaks = c(
      "Patient-based data ('standard protocol')",
      "Unit-based data ('light protocol')"
    )
  ) +
  coord_sf(xlim = c(-25, 45), ylim = c(34, 72), expand = FALSE) +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.direction = "vertical",
    legend.box = "vertical",
    legend.justification = "left",
    legend.title = element_text(face = "bold"),
    legend.background = element_rect(fill = "white", color = "#BDBDBD"),
    legend.key.height = unit(0.6, "cm"),
    legend.key.width  = unit(0.6, "cm"),
    plot.margin = margin(5, 5, 5, 5)
  ) +
  guides(fill = guide_legend(ncol = 1))

```
## Characteristics of participating ICUs
The speciality of the participating ICUs is shown in @tbl-icu-characteristics.      

The median size of the participating ICUs was `r median(as.numeric(allunits$UnitSize),na.rm=TRUE)` beds ranging from  `r min(as.numeric(allunits$UnitSize),na.rm=TRUE)` to `r max(as.numeric(allunits$UnitSize),na.rm=TRUE)`.   

```{r}
#| label: tbl-icu-characteristics
#| tbl-cap: "Characteristics of intensive care units by country/network"

library(gt)
library(dplyr)

# helper: sort A-Z and keep EU/EEA last
sort_with_eu_last <- function(df, country_col = "ReportingCountry", eu = "EU/EEA") {
  df %>%
    mutate(.is_eu = .data[[country_col]] == eu) %>%
    arrange(.is_eu, .data[[country_col]]) %>%
    select(-.is_eu)
}

eu_unit <- allunits %>%
  summarise(
    ReportingCountry = "EU/EEA",
    N = n(),
    unit_size_median = median(as.numeric(UnitSize), na.rm = TRUE),
    Spec_med  = 100 * mean(UnitSpecialty == "MED", na.rm = TRUE),
    Spec_sur  = 100 * mean(UnitSpecialty == "SURG", na.rm = TRUE),
    Spec_mix  = 100 * mean(UnitSpecialty == "MIX", na.rm = TRUE),
    Spec_coro = 100 * mean(UnitSpecialty == "CORO", na.rm = TRUE),
    Spec_ounk = 100 * mean(UnitSpecialty %in% c("O","Unk","NEU","BURN","PED","NEON"), na.rm = TRUE)
  )


icu_tbl <- country_unit_table |>
  label_country_values("ReportingCountry") |>
  bind_rows(eu_unit) |>
  sort_with_eu_last("ReportingCountry")


icu_gt <- icu_tbl |>
  gt() |>
  apply_gt_labels(icu_tbl) |>
  tab_spanner(
    label = md("**Type of ICU (%)**"),
    columns = c(Spec_med, Spec_sur, Spec_mix, Spec_coro, Spec_ounk)
  ) |>
  fmt_number(columns = c(N, unit_size_median), decimals = 0, sep_mark = " ") |>
  fmt_number(columns = c(Spec_med, Spec_sur, Spec_mix, Spec_coro, Spec_ounk), decimals = 1) |>
  sub_missing(everything(), missing_text = "NA") |>
  style_gt_common(data = icu_tbl)

icu_gt
```

## Patient demographics, risk factors on admission and cumulative incidence of healthcare-associated infections
Of `r nrow(haiicu_pt_unit)` patients staying in an ICU for more than two days (patient-based data)(@tbl-patient-demographics), `r haiicu_pt_inf_all%>%filter(hasHai==TRUE)%>%distinct(Id,.keep_all=TRUE)%>%nrow()` patients (`r round((haiicu_pt_inf_all%>%filter(hasHai==TRUE)%>%distinct(Id,.keep_all=TRUE)%>%nrow())/nrow(haiicu_pt_unit), digits=3) * 100`%) presented with at least one HAI.

```{r}
#| label: tbl-patient-demographics
#| tbl-cap: "Patient demographics and risk factors on admission by country/network"

eu_demogr <- haiicu_pt_unit %>%
  summarise(
    ReportingCountry = "EU/EEA",
    N_pat = n(),
    patdays = sum(as.numeric(los), na.rm = TRUE),
    avg_los = round(sum(as.numeric(los), na.rm = TRUE) / n(), 1),
    Gender_F_pc = 100 * mean(Gender == "F", na.rm = TRUE),
    Age_median = round(median(as.numeric(Age), na.rm = TRUE), 1),
    SapsII_median = round(median(as.numeric(SapsII), na.rm = TRUE), 1),
    Origin_HOSP_pc = 100 * mean(PatientOrigin == "HOSP", na.rm = TRUE),
    Trauma_pc = 100 * mean(Trauma == "Y", na.rm = TRUE),
    TypeAdm_med = 100 * mean(TypeOfAdmission == "MED", na.rm = TRUE),
    TypeAdm_ssur = 100 * mean(TypeOfAdmission == "SSUR", na.rm = TRUE),
    TypeAdm_usur = 100 * mean(TypeOfAdmission == "USUR", na.rm = TRUE),
    Intub_pc = 100 * mean(Intubation == "Y", na.rm = TRUE),
    UrinCath_pc = 100 * mean(UrinaryCatheter == "Y", na.rm = TRUE),
    CVC_pc = 100 * mean(CVC == "Y", na.rm = TRUE),
    ImpImmun_pc = 100 * mean(ImpairedImmunity == "Y", na.rm = TRUE),
    AntimicrUnit_pc = 100 * mean(AntimicrobialInUnit == "Y", na.rm = TRUE),
    Outcome_D_pc = 100 * mean(OutcomeUnit == "D", na.rm = TRUE)
  )

demo_tbl <- country_demogr |>
  label_country_values("ReportingCountry") |>
  bind_rows(eu_demogr) |>
  sort_with_eu_last("ReportingCountry")

demo_gt <- demo_tbl |>
  gt() |>
  apply_gt_labels(demo_tbl) |>
  tab_spanner(
    label = md("**Type of admission (%)**"),
    columns = c(TypeAdm_med, TypeAdm_ssur, TypeAdm_usur)
  ) |>
  fmt_number(columns = c(N_pat, patdays), decimals = 0, sep_mark = " ") |>
  fmt_number(columns = c(avg_los, Age_median, SapsII_median), decimals = 1) |>
  fmt_number(
    columns = c(
      Gender_F_pc, Origin_HOSP_pc, Trauma_pc, TypeAdm_med, TypeAdm_ssur, TypeAdm_usur,
      Intub_pc, UrinCath_pc, CVC_pc, ImpImmun_pc, Outcome_D_pc
    ),
    decimals = 1
  ) |>
  sub_missing(everything(), missing_text = "NA") |>
  style_gt_common(data = demo_tbl)|>
  gt::cols_width(
    c(N_pat, patdays) ~ gt::px(110)
  ) |>
  gt::tab_style(
    style = gt::cell_text(whitespace = "nowrap"),
    locations = gt::cells_body(columns = c(N_pat, patdays))
  ) |>
  gt::tab_options(
    table.font.size = gt::px(14)
  )

demo_gt
```


