---
title: "ICU-acquired pneumonia in HAIICU 2023"
format: html
---

```{r}
#| label: setup
#| include: false
#| cache: false

library(dplyr)
library(knitr)

source("../../R/_report_setup.r")
source("../../R/_lookups.r")


```
## ICU-acquired pneumonia
Of `r sum(grepl("PN",haiicu_pt_inf_all$InfectionSite))` cases of pneumonia reported, `r round(sum(haiicu_pt_inf_all$Intubation=="Y" & grepl("PN",haiicu_pt_inf_all$InfectionSite))/sum(grepl("PN",haiicu_pt_inf_all$InfectionSite)),digits=3)*100`% were associated with intubation. Among patients staying in an ICU for more than two days, `r round(sum(grepl("PN",haiicu_pt_inf_all$InfectionSite))/sum(!haiicu_pt_inf_all$dupl_pat)*100,digits=2)`% were affected by at least one episode pneumonia. 

```{r, echo=FALSE, results='hide'}
patient_days<-sum(as.numeric(haiicu_pt_inf_all$lengthofstay[! haiicu_pt_inf_all$dupl_pat]),na.rm=TRUE)
pn<-haiicu_intub$PN
pn_cases<-sum(pn,na.rm=TRUE)
patient_days_all<-sum(as.numeric(haiicu_intub$NumPatDaysUnit2d),na.rm=TRUE)
per_intubgroup<-group_by(haiicu_intub,intubgroup)
PNinc_byintubgroup<-summarise(per_intubgroup,meanPNinc=round(mean(incdens[incdens!=Inf],na.rm=TRUE),digits=2))


```

The incidence of pneumonia was `r round(sum(grepl("PN", haiicu_pt_inf_all$InfectionSite),na.rm=TRUE)/(patient_days)*1000, digits=2)` episodes per 1000 patient days (@tbl-pn-incidence).  
```{r}
library(dplyr)
library(ggplot2)
library(scales)

bsi_plot_df <- PNinc_country %>%
  transmute(
    country = ReportingCountry,
    rate = as.numeric(PNinc)
  ) %>%
  filter(!is.na(country), !is.na(rate)) %>%
  arrange(rate) %>%
  mutate(country = factor(country, levels = country))

ggplot(bsi_plot_df, aes(x = country, y = rate)) +
  geom_segment(aes(xend = country, y = 0, yend = rate), linewidth = 0.7, color = "#9aa5b1") +
  geom_point(size = 2.8, color = "#0b6e4f") +
  coord_flip() +
  scale_y_continuous(labels = label_number(accuracy = 0.01)) +
  labs(
    x = NULL,
    y = "Pneumonia incidence per 1,000 patient-days",
    title = "ICU-acquired pneumonia incidence by country"
  ) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank())


PNinc_country_tbl_named <- PNinc_country_tbl |>
  label_country_values("ReportingCountry")|>
  mutate(.is_eu = ReportingCountry == "EU/EEA") |>
  arrange(.is_eu, ReportingCountry) |>
  select(-.is_eu)
```

```{r}
#| label: tbl-pn-incidence
#| tbl-cap: "Pneumonia incidence"

gt_tbl <- PNinc_country_tbl_named |>
  gt::gt() |>
  apply_gt_labels(PNinc_country_tbl_named) |>
  add_incidence_spanner(
    data = PNinc_country_tbl_named,
    cols = inc_cols_pn,
    title = "Pneumonia incidence density",
    unit = "(episodes per 1 000 patient-days)"
  )|>
  style_gt_common(data = PNinc_country_tbl_named)
gt_tbl

```


The mean incidence density per ICU was `r round(mean(haiicu_intub$incdens[haiicu_intub$incdens!=Inf],na.rm=TRUE), digits=2)` pneumonia episodes per 1 000 patient-days (ICU IQR:`r quantile(haiicu_intub$incdens,c(.25),na.rm=TRUE)`-`r round(quantile(haiicu_intub$incdens,c(.75),na.rm=TRUE),digits=2)` ), varying from `r as.numeric(PNinc_byintubgroup[1,"meanPNinc"])` in ICUs with less than 30% intubated patients to `r as.numeric(PNinc_byintubgroup[2,"meanPNinc"]) ` in ICUs with 30-59% intubated patients, and `r as.numeric(PNinc_byintubgroup[3,"meanPNinc"])` in ICUs with more than 60% intubated patients.


## Intubation-associated pneumonia
In patient-based surveillance, the mean device-adjusted rate was `r round(mean(round(haiicudenscountr$iapincintubdays,digits=2)),digits=2)` intubation-associated pneumonia episodes
per 1 000 intubation-days and varied between `r min(IAPtable$avgiaprate)` (`r IAPtable$ReportingCountry[IAPtable$avgiaprate==min(IAPtable$avgiaprate)]`), and `r max(IAPtable$avgiaprate)` per 1 000 intubation-days
(`r IAPtable$ReportingCountry[IAPtable$avgiaprate==max(IAPtable$avgiaprate)]`) (@tbl-iap-incidence).

```{r, echo=FALSE}

IAP_tbl_named <-IAP_tbl |>
  label_country_values("ReportingCountry")|>
  mutate(.is_eu = ReportingCountry == "EU/EEA") |>
  arrange(.is_eu, ReportingCountry) |>
  select(-.is_eu)
```

```{r}
#| label: tbl-iap-incidence
#| tbl-cap: "Intubation-associated pneumonia incidence"

gt_tbl <- IAP_tbl_named |>
  gt::gt() |>
  apply_gt_labels(IAP_tbl_named) |>
  add_incidence_spanner(
    data = IAP_tbl_named,
    cols = inc_cols_iap,
    title = "IAP incidence density",
    unit = "(episodes per 1 000 intubation-days)"
  )|>
  style_gt_common(data = IAP_tbl_named)
gt_tbl
```
 
## Microbiology of ICU-acquired pneumonia
The most frequently isolated microorganisms in ICU-acquired pneumonia episodes were *`r PNtable_group_top10_pc$Isolate[1]`*, 
followed by *`r PNtable_group_top10_pc$Isolate[2]`*, *`r PNtable_group_top10_pc$Isolate[3]`* and *`r PNtable_group_top10_pc$Isolate[4]`* (@tbl-pn-micro).

```{r} 
#| label: tbl-pn-micro 
#| tbl-cap: "Distribution of the 10 most frequently isolated microorganisms in ICU-acquired pneumonia  episodes by country/network"
#| 
PNtable_group_top10_pc %>%
  label_country_columns() %>%
  gt::gt()
```

 
